Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-07 paper/main.tex
moved detailed behavioral results to supplement; added summary behavioral figures to main text
writing up behavioral results [WIP]

@@

\section*{Results}
Before testing our main hypothesis, we first examined the behavioral
data from each memory task.  We expected that the general trends and
tendancies in the behavioral data would follow previously reported
behaviors from similar tasks that had been utilized in prior work.  We
were also interested in characterizing the variability in task
performance across participants.  For example, if all participants
exhibited near-identical behaviors or performance on a given task, we
would be unable to identify how memory performance varied with
mental health or exercise.

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/free_recall_behavior}
\caption{\textbf{Free recall behavioral results.}}
\label{fig:fr_behavioral}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/naturalistic_recall_behavior}
\caption{\textbf{Naturalistic recall behavioral results.}}
\label{fig:nat_behavioral}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figs/vocab_learning_behavior}
\caption{\textbf{Foreign language vocabulary learning behavioral results.}}
\label{fig:vocab_behavioral}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
\caption{\textbf{Spatial learning behavioral results.}}
\label{fig:spatial_behavioral}
\end{figure}

>>>>

\newcommand{\frDetail}{S1}
\newcommand{\natDetail}{S2}
\newcommand{\vocabDetail}{S3}
\newcommand{\spatialDetail}{S4}

@@

\section*{Results}
Before testing our main hypothesis we examined the behavioral data
from each of four memory tasks: a random word list learning ``free
recall'' task; a naturalistic recall task whereby participants watched
a short video and then recounted the narrative; a foreign language
``flashcards'' task; and a spatial learning task.  Each of the first
three tasks (free recall, naturalistic recall, and the flashcards
task) included both an immediate (short term) memory test and a
delayed (long term) memory test.  The spatial learning task included
only an immediate test. Participants in all four tasks exhibited
general trends and tendancies that have been previously reported in
prior work.  We were also interested in characterizing the variability
in task performance across participants.  For example, if all
participants exhibited near-identical behaviors or performance on a
given task, we would be unable to identify how memory performance on
that task varied with mental health or exercise.

When participants engaged in free recall of random word lists, they
displayed strong primacy and recency effects~\citep{Murd62a} on the
immediate memory tests (as reflected by improved memory for early and
late list items; Fig.~\ref{fig:immediate_behavior}a, left and right
panels).  On the delayed memory test, the recency effect was
substantially diminished (Fig.~\ref{fig:delayed_behavior}a, left and
right panels), consistent with myriad previous studies~\citep[for
review see][]{Kaha12}.  Participants also tended to cluster their
recalls according to the words' study positions~\citep{Kaha96} on both
the immediate (Fig.~\ref{fig:immediate_behavior}a, middle panel) and
delayed (Fig.~\ref{fig:delayed_behavior}a, middle panel) memory tests.

When participants engaged in naturalistic recall by recounting the
narrative of a short story video, they reliably and accurately
remembered the major narrative events on both the immediate
(Fig.~\ref{fig:immediate_behavior}b) and delayed
(Fig.~\ref{fig:delayed_behavior}b) tests.  This is consistent with
prior work showing that memory for rich narratives is both detailed
and accurate~\citep{HeusEtal21, ChenEtal17}.

We expected (and found) that the general trends and
tendancies in the behavioral data followed previously reported
behaviors from similar tasks that had been utilized in prior work.

In Figure~\ref{fig:immediate_behavior}, we summarize participants'
behaviors on four immediate (short term) memory tests: free recall
(Fig.~\ref{fig:immediate_behavior}a), a naturalistic recall task
(Fig.~\ref{fig:immediate_behavior}b), a foreign language vocabularly
learning task (Fig.~\ref{fig:immediate_behavior}c), and a spatial
learning task (Fig.~\ref{fig:immediate_behavior}d).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/behavior_overview_immediate}
\caption{\textbf{Immediate memory tests.}}
\label{fig:immediate_behavior}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/behavior_overview_delayed}
\caption{\textbf{Delayed memory tests.}}
\label{fig:delayed_behavior}
\end{figure}
